### 2019-08-11 thesis.tex
*** empty log message ***

As described above, particles ejected by the Sun determine the overall
dynamics of the interplanetary space until the termination shock boundary.
Beyond this limit, the solar wind still has a significant influence on
the nature of the local interstellar space for a long distance up to the
heliopause. As a well established scientific discipline, solar and space
physics work towards developing a better understanding of the Sun and
the solar processes molding this vast and complex dynamic system called
heliosphere; where, within, very close to its most influential object,
lies our home planet - Earth.

\subsection{Solar and space physics research}
\label{topics}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
    \caption{ESA's past, present, and future science missions for studying the solar system.}
      {\footnotesize Credit:}
      \href{https://www.esa.int/spaceinimages/Images/2019/02/ESA_s_fleet_of_Solar_System_explorers}
      {\footnotesize ESA}{\footnotesize , accessed at 10/08/2019.}
    \label{figD1}
  \end{center}
\end{figure}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{hso_fleet_chart_april_2019.pdf}
    \caption{NASA's present and future heliophysics system observatory. The number
      between parenthesis under the probe's name is the total number of spacecrafts
      that compose the mission.}
      {\footnotesize Credit:}
      \href{https://science.nasa.gov/heliophysics}
      {\footnotesize NASA}{\footnotesize , accessed at 10/08/2019.}
    \label{figD1}
  \end{center}
\end{figure}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{corona2017.png}
    %\includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
    \caption{Solar corona captured during the total solar eclipse of 2017.
      {\footnotesize Credit:}
      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
    \label{figD2}
  \end{center}
\end{figure}

>>>>

Inside the heliosphere, objectives of solar and space physics are
understanding the evolution and dynamics of the Sun,

\subsection{Solar and space physics research}
\label{sec:topics}

As described above, particles ejected by the Sun determine the overall
dynamics of the interplanetary medium until the termination shock boundary.
Beyond this limit, the solar wind still has a significant influence on
the nature of the local interstellar space for a long distance up to the
heliopause. As a well established scientific discipline, solar and space
physics work towards developing a better comprehension of the Sun and
the solar processes molding this vast and complex dynamic system called
heliosphere.

% ; where, within, very close to its most influential object,
% lies our home planet - Earth.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
    \caption{ESA's past, present, and future science missions for studying the solar system.}
      {\footnotesize Credit:}
      \href{https://www.esa.int/spaceinimages/Images/2019/02/ESA_s_fleet_of_Solar_System_explorers}
      {\footnotesize ESA}{\footnotesize , accessed at 10/08/2019.}
    \label{esa}
  \end{center}
\end{figure}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{hso_fleet_chart_april_2019.pdf}
    \caption{NASA's present and future heliophysics system observatory. The number
      between parenthesis under the probe's name is the total number of spacecrafts
      that compose the mission.}
      {\footnotesize Credit:}
      \href{https://science.nasa.gov/heliophysics}
      {\footnotesize NASA}{\footnotesize , accessed at 10/08/2019.}
    \label{nasa}
  \end{center}
\end{figure}

\subsection{The Sun and its effects on the near-Earth environment}
\label{sec:sun}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{corona2017.png}
    %\includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
    \caption{Solar corona captured during the total solar eclipse of 2017.
      {\footnotesize Credit:}
      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
    \label{corona}
  \end{center}
\end{figure}
